---
title: "Obtaining Data"
author: "ASRS"
date: "1/6/2020"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library('AZASRS')
library('tidyverse')
```


### NAV daily  

  - `return_tibble` is important if you are joining. `FALSE` returns a SQL object rather than a tibble
```{r}
get_pm_nav_daily(return_tibble = TRUE) %>% head(5)
# However, in this case, the default is TRUE so it is not needed
```


### Cash flow daily  

  - `return_tibble` is important if you are joining. `FALSE` returns a SQL object rather than a tibble
```{r}
get_pm_cash_flow_daily(return_tibble = FALSE) %>% head(5)
```


### Fund Info  

  - Caution, this returns ALL columns, which you should limit if possible
```{r}
get_pm_fund_info() %>% head(5)
```


### Benchmarks

  - For large queries (like benchmarks) it's important to filter data
  - Requires a connection directly to DB
```{r}
con = AZASRS_DATABASE_CONNECTION()
get_benchmark_daily_index(con, return_tibble = FALSE) %>% 
  filter(effective_date >= '2018-01-01') %>%
  as_tibble() %>%
  head(10)
```


### Calculate grouped IRR's  

All settings are adjustable  


```{r}
nav = get_pm_nav_daily() %>% dplyr::filter(nav != 0)
cf = get_pm_cash_flow_daily() %>% dplyr::filter(cash_flow != 0)
pm_fund_info = get_pm_fund_info()
start_date = '2019-09-30'
end_date = '2019-12-31'
itd = FALSE
cash_adjusted = FALSE
```


#### Pulling portfolio level data
```{r}
final_data = build_grouped_irrs(start_date = start_date, end_date = end_date, itd = itd,
                                cash_adjusted = cash_adjusted, pm_fund_info = pm_fund_info,                                 pm_fund_portfolio)
final_data %>%
  head()
```


#### Pulling portfolio + category data
```{r}
final_data = build_grouped_irrs(start_date = start_date, end_date = end_date, itd = itd,
                                cash_adjusted = cash_adjusted, pm_fund_info = pm_fund_info,                                 pm_fund_portfolio, pm_fund_category_description)

final_data %>%
  head()
```


#### Pulling portfolio + category + fund data
```{r}
final_data = build_grouped_irrs(start_date = start_date, end_date = end_date, itd = itd,
                                cash_adjusted = cash_adjusted, pm_fund_info = pm_fund_info,                                 pm_fund_portfolio, pm_fund_category_description, pm_fund_common_name)

final_data %>%
  head()
```


#### Aggregation options can be seen from the pm_fund_info table:
```{r}
pmfi = get_pm_fund_info()

colnames(pmfi)
```

