---
title: "Obtaining Data"
author: "ASRS"
date: "1/6/2020"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library('AZASRS')
library('tidyverse')
```


### NAV daily  

  - `return_tibble` is important if you are joining. `FALSE` returns a SQL object rather than a tibble
```{r}
get_pm_nav_daily(return_tibble = TRUE) %>% head(5)
# However, in this case, the default is TRUE so it is not needed
```


### Cash flow daily  

  - `return_tibble` is important if you are joining. `FALSE` returns a SQL object rather than a tibble
```{r}
get_pm_cash_flow_daily(return_tibble = FALSE) %>% head(5)
```


### Fund Info  

  - Caution, this returns ALL columns, which you should limit if possible
```{r}
get_pm_fund_info() %>% head(5)
```


### Benchmarks

  - For large queries (like benchmarks) it's important to filter data
  - Requires a connection directly to DB
```{r}
con = AZASRS_DATABASE_CONNECTION()
get_benchmark_daily_index(con, return_tibble = FALSE) %>% 
  filter(effective_date >= '2018-01-01') %>%
  as_tibble()
```


