---
title: "Finding NAV by Roll Up"
output: pdf_document
---


```{r, warning=FALSE, message=FALSE}
library(AZASRS)
library(tidyverse)
```


# Find the latest NAV by any grouping

Highlighting the importance of `get_pm_nav_daily()` when looking for the latest NAV value


### All NAV data since the beginning of time
```{r}
nav = get_pm_nav_daily()
nav
```
### Filter only most recently reported NAV date

**(removing all 0 NAV funds)**
**Not Cash Adjusted** -- will only find reported values

#### At the fund level
```{r}
latest_fund_nav = nav %>%
  filter(nav != 0) %>%
  group_by(pm_fund_id) %>%
  filter(effective_date == max(effective_date)) %>%
  ungroup()
latest_fund_nav
```


#### At the portfolio level 

```{r}
latest_portfolio_nav = nav %>%
  filter(nav != 0) %>%
  group_by(pm_fund_portfolio) %>%
  filter(effective_date == max(effective_date)) %>%
  summarize(effective_date =  max(effective_date), NAV = sum(nav)) %>%
  ungroup()
latest_portfolio_nav
```


#### At the category levels, also show portfolio

```{r}
latest_category_nav = nav %>%
  filter(nav != 0) %>%
  group_by(pm_fund_portfolio, pm_fund_category_description) %>%
  filter(effective_date == max(effective_date)) %>%
  summarize(effective_date =  max(effective_date), NAV = sum(nav)) %>%
  ungroup()
latest_category_nav
```



# Finding NAV based off of specific date

Utilizing `effective_date` of `2019-12-31`


#### At the portfolio level 

```{r}
latest_portfolio_nav = nav %>%
  filter(nav != 0) %>%
  group_by(pm_fund_portfolio) %>%
  filter(effective_date == '2019-12-31') %>%
  summarize(effective_date =  max(effective_date), NAV = sum(nav)) %>%
  ungroup()
latest_portfolio_nav
```


