---
title: "Finding Cashflow by Roll Up"
output: pdf_document
---

```{r, warning=FALSE, message=FALSE}
library(AZASRS)
library(tidyverse)
```


# Find the latest cashflow by any grouping

Highlighting the importance of `get_pm_cash_flow_daily()` when looking for the latest CF value


### All CF data since the beginning of time
```{r}
cf = get_pm_cash_flow_daily()
cf
```

### Filter only most recently reported CF date

**(removing all 0 CF funds)**
**Not Cash Adjusted** -- will only find reported values

#### At the fund level
```{r}
latest_fund_cf = cf %>%
  filter(cf != 0) %>%
  group_by(pm_fund_id) %>%
  filter(effective_date == max(effective_date)) %>%
  ungroup()
latest_fund_cf
```


#### At the portfolio level 

```{r}
latest_portfolio_cf = cf %>%
  filter(cf != 0) %>%
  group_by(pm_fund_portfolio) %>%
  filter(effective_date == max(effective_date)) %>%
  summarize(effective_date =  max(effective_date), CF = sum(cash_flow)) %>%
  ungroup()
latest_portfolio_cf
```


#### At the category levels, also show portfolio

```{r}
latest_category_cf = cf %>%
  filter(cf != 0) %>%
  group_by(pm_fund_portfolio, pm_fund_category_description) %>%
  filter(effective_date == max(effective_date)) %>%
  summarize(effective_date =  max(effective_date), CF = sum(cash_flow)) %>%
  ungroup()
latest_category_cf
```



# Finding CF based off of specific date

Utilizing `effective_date` of `2019-12-31`


#### At the portfolio level 

```{r}
specific_date_portfolio_cf = cf %>%
  filter(cf != 0) %>%
  group_by(pm_fund_portfolio) %>%
  filter(effective_date == '2019-12-31') %>%
  summarize(effective_date =  max(effective_date), CF = sum(cash_flow)) %>%
  ungroup()
specific_date_portfolio_cf
```


## Between a range of dates

Between `effective_date` of `2007-01-01` and `2014-12-31`

```{r}
range_portfolio_cf = cf %>%
  filter(cf != 0) %>%
  group_by(pm_fund_portfolio, pm_fund_category_description) %>%
  filter(effective_date >= '2007-01-01' & effective_date <= '2014-12-31') %>%
  summarize(effective_date = effective_date, CF = sum(cash_flow)) %>%
  ungroup()
range_portfolio_cf
```

# grouped by quarter, choose arbitrary amount
